% Context: to send to Yale physics labs for a summer position

% Programming xp - Haskell, Python, some website design
% Inquiries should include a short resume and a description of any experience with coding, data analysis, and previous work either in a research lab or with equipment (i.e., fixing cars or computers, or building robotics for competitions, or anything similar).

% % %

\documentclass[11pt]{article}

% font! the second package determines it
\usepackage[T1]{fontenc}
\usepackage[tt=false]{libertine}

\usepackage[libertine]{newtxmath}

\usepackage[varqu, scaled=0.95]{zi4}

\usepackage[margin = 0.8in]{geometry}

\usepackage{microtype}

\usepackage{fancyhdr}
\pagestyle{empty}

\setlength{\parindent}{0em}
\setlength{\parskip}{2mm}

\usepackage{xcolor}

% makes links work and look good
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan
}

% ***The following all comes from Ziv:

\usepackage{titlesec}
\usepackage{booktabs}
% I forget if booktabs is needed for \heavyrulewidth and \lightrulewidth, but you can just put your own values there, too.

\titleformat{\section}[block]
  {\titlerule[\heavyrulewidth]\vspace{-3pt}\normalfont\bfseries\sffamily\Large}
  {}{0pt}{}[\vspace{0pt}%{\titlerule[\lightrulewidth]}
  ]

% I also use this for the spacing
\titlespacing*{\section}{0pt}{\medskipamount}{\smallskipamount}

% ***The above all came from Ziv:


\newcommand{\entry}[3]{
    \vspace{-.58em}
    \textbf{#1} \hfill \textit{#2} \\
    #3 \vspace{0.5em}}

\newcommand{\header}[1]{
    \vspace{1em}
    \titlerule[\heavyrulewidth]
    \vspace{-.1em}
    \textbf{\Large #1}
    \vspace{.4em}
    \hrule
    \vspace{0.1em}}

% following command exists because letters that reach down, like p, push the horizontal line lower
\newcommand{\headerp}[1]{
    \vspace{1em}
    \hrule
    \vspace{-.1em}
    \textbf{\Large #1}
    \vspace{.15em}
    \hrule
    \vspace{.6em}}

\begin{document}

\begin{center}

  \text{\LARGE Noam Scully}
  
  \vspace{-.1em}
  \hspace{1.8em}
  noam.scully@yale.edu $\, \bullet \,$ \href{https://noamscully.github.io}{https://noamscully.github.io}

\end{center}

\section*{Education}
\vspace{-0.1em}

\textbf{Yale University} \ \textit{Pursuing Intensive B.S.\ in Mathematics.} GPA: 3.78/4.0 \hfill \textit{New Haven, CT, Class of 2025}

\vspace{-.6mm}
\textit{Math courses:} linear algebra, real \& complex analysis, vector analysis and manifolds, group theory, Lie theory, measure theory and fourier series, representation theory, Galois theory, commutative algebra, category theory
\newline \vspace{-3.6mm} \newline
\textit{Other selected courses:} quantum mechanics I \& II, quantum information and computation, quantum error correction and fault tolerance, introductory mechanics and electricity \& magnetism, algorithms

\vspace{-.4mm}
\vspace{.1em}
\textbf{Brookline High School} \ GPA: 4.0/4.0 \hfill \textit{Brookline, MA, Class of 2020}
\vspace{.4em}


\section*{Research}
\vspace{.58em}
\vspace{-0.1em}

\entry{Visiting Scholar at Boston Univeristy Condensed Matter Theory}{Summer 2024}{
  Theoretical condensed matter physics research on using the Wigner-Weyl transform for semiclassical approximations. Mentored by Dr.\ Anatoli Polkovnikov at Boston University.
}

\entry{Final Research Project for Independent Study in Category Theory}{Spring 2024}{
	Studied category theory with Dr.\ Pablo Boixeda Alvarez of Yale University, concluding with an original research project establishing a category-theoretic generalization of measures and integration. %\href{https://bit.ly/3AADLfn}{https://bit.ly/3AADLfn}.
}

\entry{Summer Undergraduate Math Research at Yale (SUMRY REU)}{Summer 2023}{
  Geometry and dynamics research, studying saddle connections on translation surfaces with Dr.\ Taylor McAdam of Pomona College and Dr.\ Fernando Al Assal of the Max Planck Institute. Paper in preparation. %Preprint: LINK.
}

\entry{Yale College First-Year Summer Research Fellowship in the Sciences \& Engineering}{Summer 2022}{
  Astrophysics research on how feedback affects dark matter halos with Dr.\ Daisuke Nagai at Yale University.
}

\entry{Polymath Jr.\ Research Experience for Undergraduates}{Summer 2021}{
  Combinatorics research on lexicographically-least infinite square-free words, mentored by Dr.\ Eric Rowland of Hofstra University. Published in The Electronic Journal of Combinatorics: \href{https://doi.org/10.37236/11659}{https://doi.org/10.37236/11659}.
}


\section*{Teaching}
\vspace{.58em}
\vspace{-0.1em}

\entry{Yale Poorvu Center for Teaching and Learning -- ULA and Private Tutor}{2023--}{
  Undergraduate Learning Assistant (ULA) for linear algebra and real analysis, holding office hours and running proof workshops. Private tutor in linear algebra and group theory.
}

\entry{Art of Problem Solving -- Online Staff Member}{2020-21}{
  Classroom assistant, message board moderator, and grader for online math classes.
}


\section*{Extracurriculars, Skills, and Service}
\vspace{0.58em}
\vspace{-0.1em}

\entry{Coding Experience}{}{
  Familiar with Python, Haskell, \LaTeX, HTML/CSS, and Mathematica.
}

\entry{Yale Math Department Student Advisory Committee (SAC)}{2024--}{
  Volunteer with the Yale Math Department to improve the math major and foster community.
}

\entry{\textit{The Purple Crayon of Yale} Improv Comedy}{2021--}{
  Served as director, treasurer, and tour organizer.
}

\entry{Grace Hopper Search Advisory Committee for Next Head of College}{2024}{
  Student representative on the search committee for hiring the next Head of Grace Hopper College at Yale.
}

% no space for phone banking or BHS coaching - or Klezmer!?
\iffalse
\entry{Yale Student Klezmer Band}{2021--}{
   Accordionist and former president.
}

\entry{Brookline High School -- Math Center Coach and Writing Center Coach}{2018-20}{
  \vspace{-1em}
}

\entry{North Carolina Democratic Party}{2020}{
  Volunteered in a phone bank to educate voters and assist with casting absentee ballots in North Carolina.
}
\fi

\end{document}
